
Microsimulation model: Code adapted from Krijkamp et al 2018
Intervention: Proposed practice - Shift in clinical practice
Comparator: Current practice - conservative practice
  
# Load packages
```{r setup, include=FALSE}
rm(list = ls())  # remove any variables in R's memory
# Load libraries
library(tidyverse)
library(readxl)
library(SciViews)
# library(dampack)
library(dplyr)
library(writexl)
library(parallel)
library(doParallel)
library(reshape2)
library(cowplot)
library(ggrepel)
```

# Setting
```{r}
v_names_str <- c("Current clinical practice", "Shift in clinical practice")
```

# Directories

```{r}
modelsloc <- 'C:/Users/kshah/OneDrive - The University of Sydney (Staff)/Markov vs microsim/Model/Microsim model'
inputsloc <- 'C:/Users/kshah/OneDrive - The University of Sydney (Staff)/Markov vs microsim/Model/Inputs/'
results_shift <- 'C:/Users/kshah/OneDrive - The University of Sydney (Staff)/Markov vs microsim/Model/Model results/PSA results microsim/Shift'
results_current <- 'C:/Users/kshah/OneDrive - The University of Sydney (Staff)/Markov vs microsim/Model/Model results/PSA results microsim/Current'

figuresloc <- 'C:/Users/kshah/OneDrive - The University of Sydney (Staff)/Markov vs microsim/Model/Figures'

monster_shift <- "P:/Markov vs microsim/Model/Model results/PSA results microsim/Shift"
monster_current <- "P:/Markov vs microsim/Model/Model results/PSA results microsim/Current"
```

# PSA results of shift in clinical practice 
```{r}
# ## Set number of simulations
# loops <- 500
# 
# ## Combine results into a single dataset
# psa_simulation_results_shift1 <- NULL
# 
# for (loop in 1:loops) {
#   print(paste0("Dataset ", loop, " of ", loops))
#   
#   # Construct the file path
#   file_path <- file.path(monster_shift, paste0("sim_shift_clinical_practice_", loop, ".RData"))
#   
#   # Check if the file exists to avoid reading errors
#   if (file.exists(file_path)) {
#     # Load the .Rds file
#     psa_results <- readRDS(file_path)
#   # Append the loaded data to the list
#     psa_simulation_results_shift1[[loop]] <- psa_results
#   } else {
#     print(paste0("File not found: ", file_path))
#   }
# }
# 
# ## Set number of simulations
# loops <- 1000
# 
# ## Combine results into a single dataset
# psa_simulation_results_shift2 <- NULL
# 
# for (loop in 500:loops) {
#   print(paste0("Dataset ", loop, " of ", loops))
#   
#   # Construct the file path
#   file_path <- file.path(results_shift, paste0("sim_shift_clinical_practice_", loop, ".RData"))
#   
#   # Check if the file exists to avoid reading errors
#   if (file.exists(file_path)) {
#     # Load the .Rds file
#     psa_results_2 <- readRDS(file_path)
#   # Append the loaded data to the list
#     psa_simulation_results_shift2[[loop]] <- psa_results_2
#   } else {
#     print(paste0("File not found: ", file_path))
#   }
# }
# 
# # Combine the two lists into one
# combined_psa_results_shift <- c(psa_simulation_results_shift1[1:500], psa_simulation_results_shift2[501:1000])
# 
# save(file = file.path(results_shift, paste0("combined_psaresults_", gsub("-", "", Sys.Date()), ".RData")),
#      combined_psa_results_shift)

load(file = file.path(results_shift,  "combined_psaresults_20240513.RData"))
```

# PSA results of current clinical practice 
```{r}
# ## Set number of simulations
# loops <- 500
# 
# ## Combine results into a single dataset
# psa_simulation_results_current1 <- NULL
# 
# for (loop in 1:loops) {
#   print(paste0("Dataset ", loop, " of ", loops))
#   
#   # Construct the file path
#   file_path <- file.path(monster_current, paste0("sim_current_clinical_practice_", loop, ".RData"))
#   
#   # Check if the file exists to avoid reading errors
#   if (file.exists(file_path)) {
#     # Load the .Rds file
#     psa_results <- readRDS(file_path)
#   # Append the loaded data to the list
#     psa_simulation_results_current1[[loop]] <- psa_results
#   } else {
#     print(paste0("File not found: ", file_path))
#   }
# }
# 
# ## Set number of simulations
# loops <- 1000
# 
# ## Combine results into a single dataset
# psa_simulation_results_current2 <- NULL
# 
# for (loop in 500:loops) {
#   print(paste0("Dataset ", loop, " of ", loops))
#   
#   # Construct the file path
#   file_path <- file.path(results_current, paste0("sim_current_clinical_practice_", loop, ".RData"))
#   
#   # Check if the file exists to avoid reading errors
#   if (file.exists(file_path)) {
#     # Load the .Rds file
#     psa_results_2 <- readRDS(file_path)
#   # Append the loaded data to the list
#     psa_simulation_results_current2[[loop]] <- psa_results_2
#   } else {
#     print(paste0("File not found: ", file_path))
#   }
# }

# Combine the two lists into one
# combined_psa_results_current <- c(psa_simulation_results_current1[1:500], psa_simulation_results_current2[501:1000])
# 
# save(file = file.path(results_current, paste0("combined_psaresults_", gsub("-", "", Sys.Date()), ".RData")),
     # combined_psa_results_current)

load(file = file.path(results_current,  "combined_psaresults_20240513.RData"))

```

# Extract total costs and total effects
```{r}
# Create a function to extract costs
extract_tc_hat <- function(sim_result) {
  if("tc_hat" %in% names(sim_result)) {
    return(sim_result$tc_hat)
  } else {
    return(null)
  }
}

## costs
tc_hat_list_shift <- lapply(combined_psa_results_shift, extract_tc_hat)
tc_hat_list_current <- lapply(combined_psa_results_current, extract_tc_hat)

tc_hat_shift_df<- data.frame(tc_hat = unlist(tc_hat_list_shift))
tc_hat_current_df<- data.frame(tc_hat = unlist(tc_hat_list_current))


# Create a function to extract effects
extract_te_hat <- function(sim_result) {
  if("te_hat" %in% names(sim_result)) {
    return(sim_result$te_hat)
  } else {
    return(null)
  }
}

# effects
te_hat_list_shift <- lapply(combined_psa_results_shift, extract_te_hat)
te_hat_list_current <- lapply(combined_psa_results_current, extract_te_hat)

te_hat_shift_df <- data.frame(te_hat = unlist(te_hat_list_shift))
te_hat_current_df <- data.frame(te_hat = unlist(te_hat_list_current))
```

# Combine costs and effects for each strategy
```{r}
df_c <- cbind(tc_hat_current_df, tc_hat_shift_df)

df_e <- cbind(te_hat_current_df, te_hat_shift_df)

```

# Visualize PSA results and CEA 
```{r}
# Define the file path
source(file.path("C:/Users/kshah/OneDrive - The University of Sydney (Staff)/Markov vs microsim/Model/Markov model/R/Functions.R"))

l_psa <- make_psa_obj(cost          = df_c, 
                      effectiveness = df_e,
                      strategies    = v_names_str)

l_psa$strategies <- v_names_str
colnames(l_psa$effectiveness)<- v_names_str
colnames(l_psa$cost)<- v_names_str

#* Vector with willingness-to-pay (WTP) thresholds.
v_wtp <- seq(0, 50000, by = 5000)

### Cost-Effectiveness Scatter plot ----
scatter <- plot.psa(l_psa) +
  ggthemes::scale_color_colorblind() +
  ggthemes::scale_fill_colorblind() +
  xlab("Effectiveness (QALYs)") +
  guides(col = guide_legend(nrow = 2)) +
  theme(legend.position = "bottom")

ggsave(filename = file.path(figuresloc, paste0("microsim_psa_scatter_plot", gsub("-", "", Sys.Date()), ".png")),
       plot = scatter)


### Incremental cost-effectiveness ratios (ICERs) with probabilistic output ----
df_out_ce_psa <- summary.psa(l_psa)

df_cea_psa <- calculate_icers(
  cost       = df_out_ce_psa$meanCost,
  effect     = df_out_ce_psa$meanEffect,
  strategies = df_out_ce_psa$Strategy
)

df_cea_psa

### Plot cost-effectiveness frontier with probabilistic output 
icers_plot <- plot.icers(df_cea_psa)

ggsave(filename = file.path(figuresloc, paste0("microsim_psa_icer_plot", gsub("-", "", Sys.Date()), ".png")),
       plot = icers_plot)

## Cost-effectiveness acceptability curves (CEACs) and frontier (CEAF) ---
ceac_obj <- ceac(wtp = v_wtp, psa = l_psa)
summary.ceac(ceac_obj)

#* CEAC & CEAF plot
ceac <- plot.ceac(ceac_obj) +
  ggthemes::scale_color_colorblind() +
  ggthemes::scale_fill_colorblind() +
  theme(legend.position = c(0.82, 0.5))

ggsave(filename = file.path(figuresloc, paste0("microsim_ceac_icer_plot", gsub("-", "", Sys.Date()), ".png")),
       plot = ceac)


```
```

